A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-17 writeup/paper.tex
Minor changes to abstract

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skills claims by measuring their ability to correct translate words, and performing geolocation to see if they come from a country where the language is spoken. Moreover, rather than posting a one-off survey, we posted large, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.  Our study resulted in the creation of bilingual dictionaries for a wide variety of languages, and acted as census of the bilingual speakers on MTurk.  We use this to recommend languages with the largest speaker populations that are good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.

>>>>

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skills claims by measuring their ability to correctly translate words, and by geolocating workers to see if they come from a country where the language is spoken. Rather than posting a one-off survey, we posted large-scale, paid tasks consisting of 1,000 assignment to translate a total of 10,000 words in each of 100 languages.  Our study ran for weeks, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilinguals workers would have seen.  Our study resulted in the creation of bilingual dictionaries for a wide variety of languages, and acted as census of the bilingual speakers on MTurk.  We use this to recommend languages with the largest speaker populations that are good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.
